---
title: "BIG APPLE"
output: slidy_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DataComputing)
library(rvest)
library(lubridate)
library(XML)
library(RCurl)
```
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
    padding-right=
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>

## Project Overview and Questions

 * Overview

Analysis of Apple's Stock Reactions to Product Releases, Important Events, and Competition

 * Question: 
 
 1.How does percent of revenue by product of the Apple company change throughout the course of history of Apple?

 2.How does Apple's stock price perform when compared against product releases and important events in its history?

**Describing the data**

> * Apple Stock price/total asset: 

> i. The variables of interest are total asset of Apple and Date, which covers from Dec,1980 to April,2015.

> ii. Although the graph seems to be simple, the process of obtaining and cleaning the data is complicated and prolonged since it involves web scraping.

```{r,echo=FALSE,warning=FALSE,include=FALSE}
URL<-"http://csimarket.com/stocks/balance.php?code=AAPL&hist=1"
txt<- getURLContent(URL)
doc<- htmlParse(txt)
numbers<- doc%>%xpathSApply('//td[@class="debeligrub2"]/strong/span', xmlValue)
Total_Assets<-numbers[11:15]
Quarter<- doc%>%xpathSApply('//td[@class="s9 zagqs sve_jedan_red"]', xmlValue)
```

----

<div class="col2">
**Apple Stock and Product Correlation**

> * The variables of interest are close price of stock of apple, date of release of the Apple products, which covers from Dec,1980 to April, 2015.

```{r,echo=FALSE,warning=FALSE,include=FALSE}
applestocks <- read.csv("http://real-chart.finance.yahoo.com/table.csv?s=AAPL&d=3&e=29&f=2016&g=d&a=11&b=12&c=1980&ignore=.csv") %>%
  mutate(appleclose=Close, Date=lubridate::ymd(Date), applevolume=Volume)
timeline <- htmlParse("http://www.timetoast.com/timelines/apple-product-release-dates")
root <- xmlRoot(timeline)
dates <- root %>% xpathSApply("//time",xmlValue)
date <- c()
for(i in 1:length(dates)){
  date <- c(date, lubridate::ymd(as.Date(dates[i], "%B %dst, %Y")))
}
desc <- root %>% xpathSApply("//td/b",xmlValue)
timeframe <- data.frame(date, desc)
```

```{r,echo=FALSE, fig.width=7}
ggplot(applestocks, aes(x=Date,y=appleclose)) + 
  geom_line() +
  geom_vline(data = timeframe, aes(xintercept = as.numeric(date), col=desc)) +
  theme(legend.text=element_text(size = 10))+ labs(title="Apple Stock Prices and Product Release Dates",x="Date", y="Stock Close", col='Event')
```

**Percent of Revenue by product of Apple Inc.**

> * The variables of interest are percent of revenue of each product and date that covers from 1997 to 2015

```{r,echo=FALSE, fig.width=7}
prod_rev <- read.csv("./appl_prod.csv")
names(prod_rev)[names(prod_rev)=="Other.products"] <- "Other"
prod_rev <- prod_rev %>%
  mutate(Category=ifelse(as.numeric(substr(Category,4,5)>50),
                         paste(19,substr(Category,4,5),"-",substr(Category,1,2),sep=""),
                         paste(20,substr(Category,4,5),"-",substr(Category,1,2),sep="")))
prod_rev <- prod_rev %>% mutate(Category=gsub("Q1$","01-01",Category))
prod_rev <- prod_rev %>% mutate(Category=gsub("Q2$","04-01",Category))
prod_rev <- prod_rev %>% mutate(Category=gsub("Q3$","07-01",Category))
prod_rev <- prod_rev %>% mutate(Category=gsub("Q4$","10-01",Category))
names(prod_rev)[names(prod_rev)=="Category"] <- "Date"
prod_rev[is.na(prod_rev)] <- 0
ggplot(prod_rev,aes(x=lubridate::ymd(Date))) +
  geom_bar(aes(weight=iPhone+iPad+iPod+Mac+Services+Other+Peripherals+Software+Music,fill='Music')) + 
  geom_bar(aes(weight=iPhone+iPad+iPod+Mac+Services+Other+Peripherals+Software,fill='Software')) + 
  geom_bar(aes(weight=iPhone+iPad+iPod+Mac+Services+Other+Peripherals, fill='Peripherals')) + 
  geom_bar(aes(weight=iPhone+iPad+iPod+Mac+Services+Other,fill='Other')) +
  geom_bar(aes(weight=iPhone+iPad+iPod+Mac+Services,fill='Services')) + 
  geom_bar(aes(weight=iPhone+iPad+iPod+Mac,fill='Mac')) + 
  geom_bar(aes(weight=iPhone+iPad+iPod,fill='iPod')) + 
  geom_bar(aes(weight=iPhone+iPad,fill='iPad')) + 
  geom_bar(aes(weight=iPhone,fill='iPhone')) +
  labs(title="Apple % of Revenue by Product", x="Date", y="% of Revenue", fill='Product') +
  scale_fill_brewer(palette = "Set1")
```
</div>

----

<div class="col2">
**Apple vs. Microsoft Stock Comparison**

```{r, echo=FALSE, fig.width=6}
applestocks <- read.csv("http://real-chart.finance.yahoo.com/table.csv?s=AAPL&d=3&e=29&f=2016&g=d&a=11&b=12&c=1980&ignore=.csv")
microsoftstocks <- read.csv("http://real-chart.finance.yahoo.com/table.csv?s=MSFT&d=3&e=30&f=2016&g=d&a=2&b=13&c=1986&ignore=.csv")
applestocks<- applestocks %>%
  mutate(appleclose=Close, Date=lubridate::ymd(Date), applevolume=Volume)
microsoftstocks<- microsoftstocks %>%
  mutate(microsoftclose=Close, Date=lubridate::ymd(Date), microsoftvolume=Volume)
joined_stocks <- microsoftstocks %>%
  select(Date, microsoftclose, microsoftvolume) %>%
  inner_join(applestocks %>% select(Date, appleclose,applevolume), by=c("Date"="Date"))
ggplot(joined_stocks, aes(x=Date)) +
  geom_line(aes(y=appleclose, color="Apple")) +
  geom_line(aes(y=microsoftclose, color="Microsoft")) +
  labs(y="Stock Close", title="Apple vs. Microsoft Stock Prices", color="Company")
```

**Timeline of Apple's Total Assets**

```{r,echo=FALSE,warning=FALSE,include=FALSE}
readvalue= 
  function(doc)
  {
    info <- doc %>% xpathSApply('//td[@class="debeligrub2"]/strong/span', xmlValue)
    info[15]
  }

add<-c()
for (i in 2:44) {
  URL<-paste0("http://csimarket.com/stocks/balance.php?code=AAPL&hist=",i)
  txt<- getURLContent(URL)
  doc<- htmlParse(txt)
  add<- c(add, readvalue(doc))
}

Total_Assets <-c(Total_Assets, add)
readdate= 
  function(doc)
  {
    info <- doc %>% xpathSApply('//td[@class="s9 zagqs sve_jedan_red"]', xmlValue)
    info[5]
  }

date<-c()
for (i in 2:44) {
  URL<-paste0("http://csimarket.com/stocks/balance.php?code=AAPL&hist=",i)
  txt<- getURLContent(URL)
  doc<- htmlParse(txt)
  date<- c(date, readdate(doc))
}
date<-c(Quarter,date)

appleassets<-data.frame(date, Total_Assets)
appleassets<- appleassets %>%
  mutate(date=gsub("[(,),.]|I|V|Quarter|", "", date))
appleassets<- appleassets %>% mutate(date=gsub(" ", "-", date))
appleassets<-appleassets %>% mutate(date=gsub('.{1}$', "", date))
appleassets[5, 1] = "Sep-27-2014"

date<-c()
month<-c()
year<-c()
for (i in 1:length(strsplit(appleassets$date, "-"))) {
  date<-c(date, strsplit(appleassets$date, "-")[[i]][2])
  month<-c(month, strsplit(appleassets$date, "-")[[i]][1])
  year<-c(year, strsplit(appleassets$date, "-")[[i]][3])
}
lan<-c("Sep", "June", "March", "Dec")
num<-c("09", "06", "03", "12")
translation<- data.frame(lan, num)
translation<-left_join(as.data.frame(month), translation, by=c("month"="lan"))
month<-translation[,2]
appleassets<- data.frame(Date=lubridate::ymd(paste0(year,"-", month, "-", date)), appleassets) %>% select(Date, Total_Assets) %>% mutate(Total_Assets=gsub(pattern = ".000$", "", Total_Assets))
TotalAssets<-gsub(pattern = ",", "", Total_Assets)
appleassets %>% mutate(Total_Assets=TotalAssets)
```

```{r,echo=FALSE, fig.width=6}
ggplot(appleassets, aes(x=Date, y=as.numeric(TotalAssets)))+geom_smooth()+labs(y="Total Assets", title="Apple's Total Assets")
```
</div>